---
title: "README"
author: "Yves Deville"
date: "2023-05-22"
output: github_document
---



# The SeaLev package

The **SeaLev** package is a R package funded by IRSN/Behrig. It is
devoted to the distribution of a Sea Level random variable (r.v.) say
$Z$ viewed as the sum of two independent r.vs $X$ and $Y$ representing
the astronomical tide and the surge. More precisely the r.vs relate to
a *tide interval* defined as the time interval separating two
consecutive astronomical low tides. Then $X$ is the astronomical
*high-tide* level and $Y$ is the so-called *skew surge* representing
the difference between the observed highest level and the astronomical
high tide level. 

- The distribution of $X$ can be regarded a perfectly known. More
  precisely, the support of $X$ is an interval $[x_{\texttt{min}}, \,
  x_{\texttt{max}}]$ where both end-points are finite and known, and 
  $X$ admits a continuous known density $f_X(x)$ on this interval. 

- By fitting a Peaks Over Threshold (POT) model from observed skew
  surges $Y_i$ one can regard the tail distribution of $Y$ as that of
  a Generalized Pareto Distribution (GPD). 

Then the tail distribution of $Z$ can be computed by convolution. 

Mind that this package is quite old since it was created during the
pre-RStudio era.

# INSTALLATION

## Using the *remotes* package

In an R session use

```{r, eval=FALSE}
library(remotes)
install_github("IRSN/SeaLev", dependencies = TRUE, auth_token = myToken)
```

where `myToken` is *your* GitHub token. This should install the
package and make it ready to use.

Mind that by default this does not build the vignette shipped with the
package (long-form documentation). To build the vignette, use instead

```{r, eval=FALSE}
install_github("IRSN/SeaLev", dependencies = TRUE, auth_token = myToken, build_vignettes = TRUE)
```
The installation will then take a longer time but the vignette will be
accessible from the help of the package (link above the "Help Pages"
section).

You can also select a specific branch or a specific commit by using
the suitable syntax for `install_github`. For instance to install the
branch `develop` use

```{r, eval=FALSE}
install_github("IRSN/SeaLev@develop", dependencies = TRUE)
```
See the **remotes** package documentation for more details.

## Clone, build and install

### Cloning the repository

You can also clone the repository to install the package.  If you do
not have yet a local `SeaLev` repository, use `git clone` to clone the
`SeaLev` repository

``` bash
git clone https://github.com/IRSN/SeaLev
```

This will create a `SeaLev` sub-directory of the current directory,
i.e. the directory from which the git command was issued. Of course
this can work only if you have the authorisation to clone.

### Installation

Move to the parent directory of your cloned repository and use the
following command from a terminal to create a tarball source file

``` bash
R CMD build SeaLev
```
This will produce a source tarball `SeaLev_x.y.z` where `x`, `y` and
`z` stand for the major, minor and patch version numbers. Then you can
install from a command line

``` bash
R CMD INSTALL SeaLev_x.y.z
```
Note that you must also have all the packages required by **SeaLev**
installed.

You can also use the **RStudio** IDE to install the package.
